EGGs are adhesive!

### 2025-03-13 calco/main.tex
minori

\begin{corollary}\label[corollary]{prop:hypadh}
	 $\hyp$ is an adhesive category.
\end{corollary}
%\begin{proof}
%	By hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, thus the thesis follows from  \Cref{thm:slice-functors} and \Cref{prop:com}.   
%\end{proof}

@@

and edges, respectively, such that  $h_1, h_2$ have no source and $h_3, h_4$ a pair nodes

@@

We extend our graphical notation of hypergraphs to labeled ones putting the label of an hyperedge $h$ inside its corresponding square.

@@

\commentato{
\todo{Se questo remark sotto non serve nel pezzo sulle equivalenze possiamo toglierlo}
\begin{remark}\label{prop:image}
	Suppose that $(f,g)\colon (l, !_{V_{\mathcal{G}}})\to (l', !_{V_{\mathcal{H}}})$ preserves input nodes. Then  if $\tau_{\mathcal{H}}(h)=g(v)$ for some $v\in V_{\mathcal{G}}$ then $h$ belongs to the image of $f$. Indeed, by hypothesis $v$ must be in the image of $\tau_{\mathcal{G}}$ and so there exists $k$ such that $\tau_{\mathcal{G}}(k)=v$. But then $\tau_{\mathcal{H}}(f(k))=g(v)$ and we can conclude that $f(k)=h$.
\end{remark}
}

@@

Forgetting the quotient part yields a functor $T\colon \EqHyp \to \hyp$ sending an hypergraph with equivalence $(E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ to $(E_{\mathcal{G}}, V_{\mathcal{G}}, s_\mathcal{G}, t_{\mathcal{G}})$.   We now explore some of its properties to deduce information on the structure of $\EqHyp$.  
%
A proof is in \Cref{proof:forghyp}.

\begin{restatable}{proposition}{fhyp}\label{prop:forghyp}  Consider the forgetful functor $T\colon \EqHyp \to \hyp$. Then it holds
	\begin{enumerate}
		\item$T$ is faithful;
		\item $T$ has a left adjoint;
		\item $T$ has a right adjoint.
	\end{enumerate}
\end{restatable}

@@

Notice that there is another functor $K: \EqHyp \to \Set$ sending $(E, V, C, s, t, q)$ to $C$, and a morphism $(h_E, h_V, h_C)$ to $h_C$. We  exploit it to compute limits and colimits in $\EqHyp$. In order to do so. A full proof of the following lemma can be found in \Cref{proof:comp}.

@@

A proof is in \Cref{proof:regmono}.
We have now all the ingredient necessary to study the adhesivity properties of $\EqHyp$.  As a first step we need to introduce a class of monos.

\noindent
\parbox{10cm}{
\begin{definition}
	We define $\pbc$ as the class of  regular monos $(h_E, h_V, h_Q)\colon \mathcal{G}\to \mathcal{H}$ in $\EqHyp$ such that the square on the right is a pullback
\end{definition}
} \hfill
	\parbox{2cm}{
	     \xymatrix@R=18pt{
	        V_\mathcal{G} \ar@{>>}[d]_{q_\mathcal{G}} \ar@{>->}[r]_{h_V}& V_\mathcal{H} \ar@{>>}[d]^{q_\mathcal{H}} \\
	        Q_\mathcal{G} \ar@{>->}[r]^{h_Q} & Q_\mathcal{{H}}
              }
         }

Now, we show that $\pbc$ is a suitable class for adhesivity. A proof is in \Cref{proof:pbmono}.

@@

We now show that key lemma for $\pbc$-adhesivity of $\EqHyp$ is. A proof is in \Cref{proof:pbstable}.

\begin{restatable}{lemma}{pbs}\label{lemma:stab}
	In $\EqHyp$, $\pbc$-pushouts are stable.
\end{restatable}

@@

Having prove stability of $\pbc$-pushouts, we now turn to prove that they are Van Kampen with respect to regular monos.
%
A proof is found in \Cref{proof:pbvk}.

\begin{restatable}{lemma}{pbvk}\label{lemma:van_kampen}
	In $\EqHyp$, pushouts along arrows in $\pbc$ are $\reg(\EqHyp)$-Van Kampen.
\end{restatable}

@@

\begin{definition}
	Let $\Sigma$ be an algebraic signature and $\mathcal{G}^{\Sigma}$ the hypergraph associated to it. A \emph{labelled hypergraph with equivalence} is a pair $(\mathcal{H}, l)$ where $\mathcal{H}$ is an object of $\EqHyp$ and $l$ a morphism $T(\mathcal{H})\to \mathcal{G}^\Sigma$ of $\EqHyp$. A \emph{morphism of labelled hypergraphs with equivalence} between $(\mathcal{H}, l)$ and $(\mathcal{H}', l')$ is an arrow $h\colon \mathcal{H}\to \mathcal{H}'$ such that $l= l'\circ T(\mathcal{H})$.

	We denote the resulting category by $\EqHyp_\Sigma$.
\end{definition}

@@

Let $V_\Sigma\colon \EqHyp_\Sigma\to \EqHyp$ be the functor forgetting the labelling and let $\pbc_\Sigma$ be the class of morphisms in $\EqHyp_\Sigma$ whose image in $\EqHyp$ is in $\pbc$. From the second point of \Cref{thm:slice-functors,prop:forghyp,lim} we can deduce the following.

\begin{proposition}\label{prop:lim}Consider the forgetful functor $V_{\Sigma}\colon \EqHyp_\Sigma\to \EqHyp$. Then it holds
	\begin{enumerate}
		\item $\EqHyp_\Sigma$ has all colimits and all connected limits, which are created by $V_{\Sigma}$;
		\item $\EqHyp_\Sigma$ is $\pbc_\Sigma$-adhesive.
	\end{enumerate}
\end{proposition}

In particular, $\EqHyp_\Sigma$ has all equalizers and pullbacks.
Using \Cref{cor:mono1,cor:mono2} we immediately get the following result.

\begin{corollary}\label{prop:monos_in_eqhyps} Let $h=(h_{E}, h_V, h_Q)$ be an arrow in $\EqHyp_\Sigma$. Then it holds
	\begin{enumerate}
		\item $h$ is mono if and only if $h_E$ and $h_V$ are injective;
		\item $h$ is a regular mono if and onky if $h_E$, $h_V$ and $h_Q$ are injective.
	\end{enumerate}
\end{corollary}

@@

\noindent
\parbox{11cm}{\hspace{15pt}Let now $\mathcal{T}$ be the class of morphism in $\EqTG_{\Sigma}$ whose image through $I_\eq$ is in $\pbc_\Sigma$ and whose image trhough $S_\Sigma$ is a regular mono in $\tg$.  Unwrapping the definition and using \Cref{lem:reg}, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill \parbox{2cm}{\xymatrix{V_{\mathcal{G}}\ar@{>->}[r]^{h_V} \ar@{>>}[d]_{q_{\mathcal{H}}}& V_{\mathcal{H}} \ar@{>>}[d]^{q_{\mathcal{H}}}\\ Q_{\mathcal{G}} \ar@{>->}[r]^{h_Q}& Q_{\mathcal{H}}} }

@@

The following proposition is now an easy corollary of \Cref{prop:push}, \Cref{prop:lim}, and \Cref{rem:obv}. We provide the details in \Cref{proof:tade}.

\begin{restatable}{proposition}{po}\label{prop:po}
$\EqTG_{\Sigma}$ has all $\mathcal{T}$-pushouts, which are created by $I_{\eq}$.
\end{restatable}

@@

\subsection{Hypergraph with closed equivalence}
\begin{definition}
	Let $\mathcal{G} = (E, V, C, s, t, q)$ be a hypergraph with equivalence and $(S, \pi_1, \pi_2)$ a kernel pair of $q^\star \circ s$.
	Then, $\mathcal{G}$ is an \emph{e-hypergraph} whenever $q^\star \circ t \circ \pi_1 = q^\star \circ t \circ \pi_2$.
	$\egg$ is the full subcategory of $\EqHyp$ whose objects are e-hypergraphs, and $I: \egg \to \EqHyp$ is the inclusion functor.
\end{definition}

\begin{lemma}
	$\egg$ has all limits and $I$ preserves them.
\end{lemma}

@@

\begin{corollary}
	$I$ creates limits.
\end{corollary}

@@

\begin{proof}\label{proof:regmono}
	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos.
	\parbox{11cm}{
	Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$. Let $e\colon E_Q\mto Q_{\mathcal{H}}$ be the equalizer in
	$\Set$ of $f_Q, g_Q\colon Q_{\mathcal{H}}\rightrightarrows Q_{\mathcal{K}}$. From the third point of \Cref{prop:fact} and \Cref{lim} we know that $h_V\colon V_{\mathcal{G}}\mto V_{\mathcal{H}} $ 
	is the equalizer of $f_V, g_V\colon V_{\mathcal{H}}\rightrightarrows V_{\mathcal{K}}$, thus by the second point of \Cref{prop:eqhyp_complete} we know that there is a mono 
	$m\colon Q_{\mathcal{G}}\mto E_Q$ fitting in the diagram aside. Now, notice that 
	$e\circ m\circ q_{\mathcal{G}}=q_\mathcal{H}\circ h_V=h_{Q}\circ q_{\mathcal{G}}$.
	Since $q_{\mathcal{G}}$ is epi we conclude that $e\circ m=h_Q$, from which the thesis follows.}
	\hfill
	\parbox{2cm}{\xymatrix@R=18pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar@{>->}[r]^{h_V}& V_\mathcal{H} \ar@{>>}[dd]^{q_{\mathcal{H}}}\\Q_\mathcal{G} \ar@{>.>}[d]_{m}&\\ E_Q \ar@{>->}[r]_{e} & Q_\mathcal{{H}}}}

@@

\pbs*

\begin{proof}\label{proof:pbstable}
	Let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'_i=(A'_i, B'_i, Q'_i, s'_i, t'_i, q'_i)$, for $i \in \{1, 2, 3, 4\}$, be hypergraphs with equivalence, 
	and that suppose in the first diagram below,  all the vertical faces are pullbacks, the bottom face is a pushout $h$ is a regular mono and $k_Q\colon Q_1\mto Q_3$ is mono. By \Cref{prop:eqhyp_complete} the same is true for the other two cubes, by \Cref{cor:mono2}, $h_E$ and $h_V$ are monos and so the top faces of these cubes are pushouts.
	\[
	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_{z_V'} \\ 
		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}
		&&B_3'  \ar[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){d_V}\\
		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
	\]

\pbvk*

\begin{proof}\label{proof:pbvk}

Consider a cube as the one below on the left, with regular monos as vertical arrows, pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is in $\pbc$.
Given \Cref{lemma:stab}, if we show that the front faces are pullbacks too we can conclude.

To fix notation, let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'=(A_i', B_i', Q_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$. By \Cref{prop:eqhyp_complete} and \Cref{cor:mono2} we know that the central and right cube below have pushouts as bottom faces and pullbacks as back faces,
	thus their front faces are pullbacks
	\[
	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar@{>->}[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar@{>->}[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar@{>->}[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar@{>->}[dd]^{b_V} \ar[dl]_{z_V'} \\ 
		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar@{>->}[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar@{>->}[dd]_(.3){d_E}
		&&B_3'  \ar@{>->}[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>->}[dd]_(.3){d_V}\\
		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
	\]

	Now we have done, since by computing we have
\[\begin{split}
	y_1\circ a_3&= q'_4\circ p'_2=p'_3 \circ q'_3=y_1\circ m_3\circ q'_3\\
u_1\circ a_2&= q'_4\circ t'_2=t'_3 \circ q'_3=u_1\circ m_2\circ q'_2 
\end{split} \qquad \begin{split}
 	y_2\circ a_3&= d_3\circ q_3'=y_2\circ m_3\circ q'_3\\
u_2\circ a_2&= d_2\circ q_2'=u_2\circ m_2\circ q'_2
\end{split}\]	
%	And we have done.
\end{proof}

>>>>

\begin{corollary}\label[corollary]{prop:hypadh}
	 $\hyp$ is an adhesive category.
\end{corollary}
\begin{proof}
	By hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, thus the thesis follows from  \Cref{thm:slice-functors} and \Cref{prop:com}.   
\end{proof}

@@

and edges, respectively, such that  $h_1, h_2$ are constants and $h_3, h_4$ are binary operators

@@

We will extend our graphical notation of hypergraphs to labeled ones putting the label of an hyperedge $h$ inside its corresponding square.

@@

\todo{Se questo remark sotto non serve nel pezzo sulle equivalenze possiamo toglierlo}
\begin{remark}\label{prop:image}
	Suppose that $(f,g)\colon (l, !_{V_{\mathcal{G}}})\to (l', !_{V_{\mathcal{H}}})$ preserves input nodes. Then  if $\tau_{\mathcal{H}}(h)=g(v)$ for some $v\in V_{\mathcal{G}}$ then $h$ belongs to the image of $f$. Indeed, by hypothesis $v$ must be in the image of $\tau_{\mathcal{G}}$ and so there exists $k$ such that $\tau_{\mathcal{G}}(k)=v$. But then $\tau_{\mathcal{H}}(f(k))=g(v)$ and we can conclude that $f(k)=h$.
\end{remark}

@@

Forgetting the quotient part yields a functor $T\colon \EqHyp \to \hyp$ which sends an hypergraph with equivalence $(E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ to $(E_{\mathcal{G}}, V_{\mathcal{G}}, s_\mathcal{G}, t_{\mathcal{G}})$.   We can now explore some of its properties to deduce some information on the structure of $\EqHyp$.

\begin{restatable}{proposition}{fhyp}\label{prop:forghyp}  The following are true:
	\begin{enumerate}
		\item$T$ is faithful;
		\item $T$ has a left adjoint;
		\item $T$ has a right adjoint.
	\end{enumerate}
\end{restatable}
A proof is provided in \Cref{proof:forghyp}.

@@

Let us notice that there is another functor $K: \EqHyp \to \Set$ sending $(E, V, C, s, t, q)$ to $C$, and a morphism $(h_E, h_V, h_C)$ to $h_C$. We are now going to exploit it to compute limits and colimits in $\EqHyp$. In order to do so. A full proof of the following lemma can be found in \Cref{proof:comp}.

@@

We have now all the ingredient necessary to study the adhesivity properties of $\EqHyp$.  As a first step we need to introduce a class of monos.

\begin{definition}
	We define $\pbc$ as the class of all regular monos $(h_E, h_V, h_Q)\colon \mathcal{G}\to \mathcal{H}$ in $\EqHyp$ such that the square on the right is a pullback
\end{definition}

We can now prove that $\pbc$ is a class suitable to prove adhesivity with respect to it (a proof can be found in \Cref{proof:pbmono}).

@@

We are now going to show that $\EqHyp$ is $\pbc$-adhesive.

\begin{lemma}\label{lemma:stab}
	In $\EqHyp$, $\pbc$-pushouts are stable.
\end{lemma}

\begin{proof}
	Let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'_i=(A'_i, B'_i, Q'_i, s'_i, t'_i, q'_i)$, for $i \in \{1, 2, 3, 4\}$, be hypergraphs with equivalence, 
	and that suppose in the first diagram below,  all the vertical faces are pullbacks, the bottom face is a pushout $h$ is a regular mono and $k_Q\colon Q_1\mto Q_3$ is mono. By \Cref{prop:eqhyp_complete} the same is true for the other two cubes, by \Cref{cor:mono2}, $h_E$ and $h_V$ are monos and so the top faces of these cubes are pushouts.
	\[
	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_{z_V'} \\ 
		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}
		&&B_3'  \ar[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){d_V}\\
		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
	\]

@@

Having prove stability of $\pbc$-pushouts, we now turn to prove that they are Van Kampen with respect to regular monos.

\begin{lemma}\label{lemma:van_kampen}
	In $\EqHyp$, pushouts along arrows in $\pbc$ are $\reg(\EqHyp)$-Van Kampen.
\end{lemma}

\begin{proof}

Consider a cube as the one below on the left, with regular monos as vertical arrows,, with pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is in $\pbc$.
In lieu of \Cref{lemma:stab}, if we show that 	the front faces are pullbacks too we can conclude.

To fix the notation, let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'=(A_i', B_i', Q_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$. By \Cref{prop:eqhyp_complete} and \Cref{cor:mono2} we know that the central and right cube below have pushouts as bottom faces and pullbacks as back faces,
	thus their front faces are pullbacks too.
	\[
	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar@{>->}[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar@{>->}[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar@{>->}[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar@{>->}[dd]^{b_V} \ar[dl]_{z_V'} \\ 
		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar@{>->}[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar@{>->}[dd]_(.3){d_E}
		&&B_3'  \ar@{>->}[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>->}[dd]_(.3){d_V}\\
		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
	\]

	Now if we compute we have:
\[\begin{split}
	y_1\circ a_3&= q'_4\circ p'_2=p'_3 \circ q'_3=y_1\circ m_3\circ q'_3\\
u_1\circ a_2&= q'_4\circ t'_2=t'_3 \circ q'_3=u_1\circ m_2\circ q'_2 
\end{split} \qquad \begin{split}
 	y_2\circ a_3&= d_3\circ q_3'=y_2\circ m_3\circ q'_3\\
u_2\circ a_2&= d_2\circ q_2'=u_2\circ m_2\circ q'_2
\end{split}\]	
	And we have done.
\end{proof}

@@

\begin{definition}
	Let $\Sigma$ be an algebraic signature and $\mathcal{G}^{\Sigma}$ the hypergraph associated to it. A \emph{labelled hypergraph with equivalence} is a pair $(\mathcal{H}, l)$ where $\mathcal{H}$ is an object of $\EqHyp$ and $l$ a morphism $T(\mathcal{H})\to \mathcal{G}^\Sigma$ of $\EqHyp$. A \emph{morphsim of labelled hypergraphs with equivalence} between $(\mathcal{H}, l)$ and $(\mathcal{H}', l')$ is an arrow $h\colon \mathcal{H}\to \mathcal{H}'$ such that $l= l'\circ T(\mathcal{H})$.

	We will denote the resulting category by $\EqHyp_\Sigma$.
\end{definition}

@@

$V_\Sigma\colon \EqHyp_\Sigma\to \EqHyp$ be the functor forgetting the labelling and let $\pbc_\Sigma$ be the class of morphisms in $\EqHyp_\Sigma$ whose image in $\EqHyp$ is in $\pbc$. From the second point of \Cref{thm:slice-functors,prop:forghyp,lim} we can deduce the following.

\begin{proposition}\label{prop:lim}The following facts hold true:
	\begin{enumerate}
		\item $\EqHyp_\Sigma$ has all colimits and all connected limits, which are created by the forgetful functor $V_{\Sigma}\colon \EqHyp_\Sigma\to \EqHyp$, in particular it has all equalizers and pullbacks;
		\item $\EqHyp_\Sigma$ is $\pbc_\Sigma$-adhesive.
	\end{enumerate}
\end{proposition}

Using \Cref{cor:mono1,cor:mono2} we immediately get the following result.

\begin{corollary}\label{prop:monos_in_eqhyps} Let $h=(h_{E}, h_V, h_Q)$ be an arrow in $\EqHyp_\Sigma$, then:
	\begin{enumerate}
		\item $h$ is mono if and only if $h_E$ and $h_V$ are injective;
		\item $h$ is a regular mono if and onky if $h_E$, $h_V$ and $h_Q$ are injective.
	\end{enumerate}
\end{corollary}

@@

\noindent
\parbox{11cm}{\hspace{15pt}Let now $\mathcal{T}$ be the class of morphism in $\EqTG_{\Sigma}$ whose image through $I_\eq$ is in $\pbc_\Sigma$ and whose image trhough $S_\Sigma$ is a regular mono in $\tg$.  Unwrapping the definition and using $\Cref{lem:reg}$, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill \parbox{2cm}{\xymatrix{V_{\mathcal{G}}\ar@{>->}[r]^{h_V} \ar@{>>}[d]_{q_{\mathcal{H}}}& V_{\mathcal{H}} \ar@{>>}[d]^{q_{\mathcal{H}}}\\ Q_{\mathcal{G}} \ar@{>->}[r]^{h_Q}& Q_{\mathcal{H}}} }

@@

The following proposition is now an easy corollary of \Cref{prop:push,prop:lim,rem:obv}. We provide the details in \Cref{proof:tade}.

\begin{restatable}{proposition}{po}\label{prop:po}
$\EqTG_{\Sigma}$ has all $\mathcal{T}$.pushouts, which are created by $I_{\eq}$.
\end{restatable}

@@

\subsection{E-hypergraphs}

We start introducing the notion of \emph{e-hypergraphs}, hypergraphs equipped with an equivalence relation which is closed under the source and target arrow. This means that whenever the relations identifies the source of an hyperedge, it identifies the targets too.

\begin{definition}
	Let $\mathcal{G} = (E, V, Q, s, t, q)$ be a hypergraph with equivalence and $(S, \pi_1, \pi_2)$ a kernel pair for $q^\star \circ s$.
	We will say that $\mathcal{G}$ is an \emph{e-hypergraph} if $q^\star \circ t \circ \pi_1 = q^\star \circ t \circ \pi_2$.

	We will denote by $\egg$ the full subcategory of $\EqHyp$ whose objects are e-hypergraphs, and by $I\colon \egg \to \EqHyp$ the associated inclusion functor.
\end{definition}

\begin{lemma}
	$\egg$ has all limits and $I$ creates them.
\end{lemma}

@@

@@

\begin{proof}
$(\Rightarrow)$	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos.
	\parbox{11cm}{
	Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$. Let $e\colon E_Q\mto Q_{\mathcal{H}}$ be the equalizer in
	$\Set$ of $f_Q, g_Q\colon Q_{\mathcal{H}}\rightrightarrows Q_{\mathcal{K}}$. From the third point of \Cref{prop:fact} and \Cref{lim} we know that $h_V\colon V_{\mathcal{G}}\mto V_{\mathcal{H}} $ 
	is the equalizer of $f_V, g_V\colon V_{\mathcal{H}}\rightrightarrows V_{\mathcal{K}}$, thus by the second point of \Cref{prop:eqhyp_complete} we know that there is a mono 
	$m\colon Q_{\mathcal{G}}\mto E_Q$ fitting in the diagram aside. Now, notice that 
	$e\circ m\circ q_{\mathcal{G}}=q_\mathcal{H}\circ h_V=h_{Q}\circ q_{\mathcal{G}}$.
	Since $q_{\mathcal{G}}$ is epi we conclude that $e\circ m=h_Q$, from which the thesis follows.}
	\hfill
	\parbox{2cm}{\xymatrix@R=18pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar@{>->}[r]^{h_V}& V_\mathcal{H} \ar@{>>}[dd]^{q_{\mathcal{H}}}\\Q_\mathcal{G} \ar@{>.>}[d]_{m}&\\ E_Q \ar@{>->}[r]_{e} & Q_\mathcal{{H}}}}

@@
